Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-08 man/figures/growth_changes.Rmd
add improvement to gc

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
```

@@

@@

custom_corrected_gc <- list(
  geom_bar(stat='identity', fill=micolor, colour=micolor),
  theme_bw(), 
  geom_hline(yintercept=c(50, -50), linetype=2, colour='black'),

>>>>

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("magrittr")
```

@@

# gc_todos %<>% mutate(yearF = as.Date(as.character(year), format="%Y"))

@@

custom_corrected_gc <- list(
  geom_bar(stat='identity', fill=micolor, colour=micolor),
  theme_bw(), 
  geom_hline(yintercept=c(50, -50), linetype=2, colour='black'),
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black',fill='white'))
  )

gccaL <- gc_todos %>% 
  filter(site == 'gc_caL') %>% 
  ggplot(aes(x=year, y=gc_md)) + 
  geom_hline(yintercept = 0, colour = 'black', lwd = 0.3) + 
  geom_errorbar(aes(ymin = gc_md - gc_md_se, ymax = gc_md + gc_md_se), colour='gray', width=.3, size=.2) + 
  # scale_y_continuous(trans = pos_neg_log) +
  # facet_wrap(~site_sorted, nrow = 2,
  #            labeller=as_labeller(c("1_caH" = "CA-High", "2_caL" = "CA-Low"))) + 
    ylab(custom_ylab) + custom_corrected_gc

gccaH <- gc_todos %>% 
  filter(site == 'gc_caH') %>% 
  ggplot(aes(x=year, y=gc_md)) + 
  geom_hline(yintercept = 0, colour = 'black', lwd = 0.3) + 
  geom_errorbar(aes(ymin = gc_md - gc_md_se, ymax = gc_md + gc_md_se), colour='gray', width=.3, size=.2) + 
  # scale_y_continuous(trans = pos_neg_log) +
  # facet_wrap(~site_sorted, nrow = 2,
  #            labeller=as_labeller(c("1_caH" = "CA-High", "2_caL" = "CA-Low"))) + 
    ylab(custom_ylab) + custom_corrected_gc

ggplot_build(gccaH)$layout$panel_scales_y[[1]]$range$range
ggplot_build(gccaL)$layout$panel_scales_y[[1]]$range$range

##### -------------------------
# VALIDO 
# NEW
th <- list(

)

custom_corrected_gc <- list(
  geom_bar(stat='identity', fill=micolor, colour=micolor),
  theme_bw(), 
  geom_hline(yintercept=c(50, -50), linetype=2, colour='black'),
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black',fill='white'))
  )

# Function for plot

plotGC <- function(df, y, yse, x, my_ylab, micolor, xrange, ...){ 
  # Get error bar aesthetic
  yerrorbar <- aes_string(ymin = paste(y, yse, sep = '-'),
                         ymax = paste(y, yse, sep = '+'))

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour='gray', width=.35, size=.3) + 
    geom_bar(stat='identity', fill=micolor, colour=micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.3) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept=c(50, -50), linetype=2, colour='black') +
    theme_bw() +
    theme(panel.grid = element_blank()) +
    # Customize limits and breaks to min of year data 
    scale_x_continuous(limits = c(min(xrange), max(xrange)), 
                       breaks = xrange, 
                       sec.axis = dup_axis())
  p
}

# Get min and max of year range and create vector of 10 years 
xrange <- seq(round(min(gc_todos$year) / 10) * 10, 
    round(max(gc_todos$year) / 10) * 10, by = 10)

gc_todos %>% dplyr::filter(site == 'gc_caH') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
       my_ylab = '% GC', micolor = "#838B8B", xrange=xrange)

gc_todos %>% dplyr::filter(site == 'gc_caL') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
       my_ylab = NULL, micolor = "#838B8B", xrange=xrange)

gc_todos %>% dplyr::filter(site != 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
       my_ylab = NULL, micolor = "#838B8B", xrange=xrange) + 
  facet_rep_wrap(~site, ncol = 1) + 
  theme(panel.spacing = unit(5, "lines"),
        strip.placement = "inside", 
        strip.background = element_blank())

##### -------------------------
# END VALIDO

# Round to the nearest decade 
# https://stackoverflow.com/questions/35352914/floor-a-year-to-the-decade-in-r 
# options (lubridate::round_date(min(gc_todos$yearF), 'years')

gccaL <- gc_todos %>% 
  filter(site == 'gc_caL') %>% 
  ggplot(aes(x=year, y=gc_md)) +

gccaL <- gc_todos %>% 
  filter(site == 'gc_caL') %>% 
  ggplot(aes(x=year, y=gc_md)) + 
  geom_hline(yintercept = 0, colour = 'black', lwd = 0.3) + 
  geom_errorbar(aes(ymin = gc_md - gc_md_se, ymax = gc_md + gc_md_se), colour='gray', width=.3, size=.2) + 
  # scale_y_continuous(trans = pos_neg_log) +
  # facet_wrap(~site_sorted, nrow = 2,
  #            labeller=as_labeller(c("1_caH" = "CA-High", "2_caL" = "CA-Low"))) + 
    ylab(custom_ylab) + custom_corrected_gc

c <- gc_todos %>% 
  filter(site != 'gc_sj') %>% 
  ggplot(aes(x=year, y=gc_md)) + 
  geom_hline(yintercept = 0, colour = 'black', lwd = 0.3) + 
  geom_errorbar(aes(ymin = gc_md - gc_md_se, ymax = gc_md + gc_md_se), colour='gray', width=.3, size=.2) + 
  # scale_y_continuous(trans = pos_neg_log) +
  facet_wrap(~site_sorted, nrow = 2,
             labeller=as_labeller(c("1_caH" = "CA-High", "2_caL" = "CA-Low"))) + 
    ylab(custom_ylab) + custom_corrected_gc

plot_medians_corregido <- d + c + plot_layout(ncol=1, heights = c(1, 2))
plot_medians_corregido
```

gc_todos <- read.csv(here::here("data/disturbance", "disturbance_gc.csv"), header = TRUE, sep = ',')

custom_corrected_gc <- list(
  geom_bar(stat='identity', fill=micolor, colour=micolor),
  theme_bw(), 
  geom_hline(yintercept=c(50, -50), linetype=2, colour='black')

### 2018-11-08 man/figures/ring_climate.Rmd
add improvement to gc

ring_climate <- p_prec_spei + theme(legend.position="none") + ptemperatura + plot_layout(ncol=1, heights = c(2,3), tag_level = 'keep')  + plot_annotation(tag_levels = c('a','b'))

>>>>

ring_climate <- p_prec_spei + theme(legend.position="none") + ptemperatura + plot_layout(ncol=1, heights = c(2,3), tag_level = 'keep')  + plot_annotation(tag_levels = c('a','b')) & theme(plot.tag = element_text(size = 20, face = 2))
